05_DESeq_manipulation

### 2019-05-20 analysis/05_DESeq2_manipulate.Rmd
now with heatmaps

```{r pheatmap, eval = F}

@@

@@

  sigDEGs <- cbind(DEGs,padjmin)

  sigDEGs <- sigDEGs %>% arrange(padjmin)
  sigDEGs <- head(sigDEGs,500)
  sigDEGs <- as.data.frame(sigDEGs)
  rownames(sigDEGs) <- sigDEGs$rownames
  drop.cols <-colnames(sigDEGs[,grep("padj|pval|pmin|rownames", colnames(sigDEGs))])
  sigDEGs <- sigDEGs %>% dplyr::select(-one_of(drop.cols))
  sigDEGs <- as.matrix(sigDEGs)
  sigDEGs <- sigDEGs - rowMeans(sigDEGs)

>>>>

```{r pheatmap, eval = T}

@@

  dds <- eachdds

@@

  sigDEGs <- cbind(DEGs,padjmin)
  sigDEGs <- sigDEGs %>% arrange(padjmin)
  sigDEGs <- head(sigDEGs,500)
  sigDEGs <- as.data.frame(sigDEGs)
  rownames(sigDEGs) <- sigDEGs$rownames
  drop.cols <-colnames(sigDEGs[,grep("padj|pval|pmin|rownames", colnames(sigDEGs))])
  sigDEGs <- sigDEGs %>% dplyr::select(-one_of(drop.cols))
  sigDEGs <- as.matrix(sigDEGs)
  sigDEGs <- sigDEGs - rowMeans(sigDEGs)
